---
title: "CapDashHelper"
output: html_document
date: "2024-07-14"
---

### CAPSTONE DASHBOARD HELPER FILE
This file was created to support the shiny dashboard application 'CapApp.R'. The code below will accomplish data uploads and data manipulations, function creations to conduct data visualization and regression analysis, and the saving of all data, uploaded and newly generated, to RDA files that can be called upon in a separate shiny app file to produce dashboard output. Ultimately, the purpose of this Rmd file is to streamline the development process of the app as well as to create a project where not only the end product is user-friendly, but also the underlying code. Well-structured and comprehensible code will facilitate ease of maintenance, encourage further development, and enable others to easily adapt and reuse portions of the code for different data sets or projects.


```{r setup, include=FALSE}

# Load required libraries
library(readr) 
library(plm)

library(dplyr)
library(tidyr)
  
library(broom)
library(zoo)
library(sandwich)
library(lmtest)

library(stargazer)


knitr::opts_chunk$set(echo = TRUE)
```

## Base Data Upload
Upload data from the Google Drive spreadsheet, which is a compilation of data from the Annual Database of Global Wine Markets (1835 to 2022), and FRED data, details and citations below. 

Anderson, K. and V. Pinilla (with the assistance of A.J. Holmes), Annual Database of Global Wine Markets, 1835 to 2022, freely available in Excel at the University of Adelaide’s Wine Economics Research Centre, December 2023

The upload sources data from tabs the following tabs:
8: Volume of wine production per capita (litres) 
12: Volume of wine export per capita (litres) 
17: Volume of wine import per capita (kilolitres)
34: Volume of beverage wine consumption (kilolitres)
38 Volume of beverage wine consumption per capita (litres) 
63: Real GDP per capita at 1990 International Geary-Khamis dollars
'Wine Consumption per adult' (gid=1192577125) computed using tabs:
34: Volume of beverage wine consumption (kilolitres)
58: Population (on July 1) 
60: Share of adults (>14 years) in population (%)


World Bank Group, DataBank, World Development Indicators, Official Exchange Rate; https://databank.worldbank.org/source/world-development-indicators/Series/PA.NUS.FCRF# 

Official exchange rate is sourced from the World Bank


```{r data_upload}

# Upload data from google drive spreadsheet


# Define the base URL
base_url <- 'https://docs.google.com/spreadsheets/d/1_MQanKGEWOBr71H3I8Z8g049GzVT94UCqmQ5SGX4_rw/export?format=csv&id=1_MQanKGEWOBr71H3I8Z8g049GzVT94UCqmQ5SGX4_rw&gid='
# Define GIDS
gids <- c('1040342295', '729504842', '780290837', '869306701', '1192577125', '1716168823', '2097958463', '799223978')
# Give names for gids
names <- c('wineproduction', 'wineexports', 'wineimports', 'realgdp', 'conperadult', 'rate', 'conpercap', 'convol' )

# Create list to store the dataframes
data_list <- list()
# Loop through the gids and import the data
for (i in seq_along(gids)) {
  url <- paste0(base_url, gids[i])
  data_list[[names[i]]] <- read_csv(url)
}

# Assign variable names 
wineproduction <- data_list$wineproduction 
wineexports <- data_list$wineexports
wineimports <- data_list$wineimports
realgdp <- data_list$realgdp
rate <- data_list$rate
conpercap <- data_list$conpercap
conperadult <- data_list$conperadult
convol <- data_list$convol

```


## Data Manipulations
Edit data so units are appropriate and consistent across comparable values. Save data as both a regular dataframe and a panel dataframe, as well as in alternative formats (either subsetted, renamed, or combined with supplemental data) designed for ease of use in generation of specific output.

# Base Dataframe and Panel Dataframe
The dataframe 'capdata' and panel dataframe 'cappdata' consist of all base data measured in appropriate units and and are the root of what we will be analyzing in this project.
```{r base_data}
# Reshape dfs to long format and proper in units
  # Convert KL data to L except convol (consumption volume) remains in KL
wineproduction_long <- wineproduction %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "WineProduction") %>%
  mutate(Year = as.numeric(Year))
wineexports_long <- wineexports %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "WineExports") %>%
  mutate(Year = as.numeric(Year))
wineimports_long <- wineimports %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "WineImports") %>%
  mutate(Year = as.numeric(Year),
         WineImports = WineImports * 1000)  # Convert kiloliters to liters
realgdp_long <- realgdp %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "RealGDP") %>%
  mutate(Year = as.numeric(Year))
rate_long <- rate %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "Rate") %>%
  mutate(Year = as.numeric(Year))
conpercap_long <- conpercap %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "ConPerCap") %>%
  mutate(Year = as.numeric(Year))
conperadult_long <- conperadult %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "ConPerAdult") %>%
  mutate(Year = as.numeric(Year),
         ConPerAdult = ConPerAdult * 1000)  # Convert kiloliters to liters
convol_long <- convol %>%
  pivot_longer(cols = starts_with("1961"):starts_with("2018"), 
               names_to = "Year", 
               values_to = "ConVol") %>%
  mutate(Year = as.numeric(Year))

# Merge data by country and year
sourcedata <- wineproduction_long %>%
  left_join(wineexports_long, by = c("Country", "Year")) %>%
  left_join(wineimports_long, by = c("Country", "Year")) %>%
  left_join(realgdp_long, by = c("Country", "Year")) %>%
  left_join(rate_long, by = c("Country", "Year")) %>%
  left_join(conpercap_long, by = c("Country", "Year")) %>%
  left_join(conperadult_long, by = c("Country", "Year")) %>%
  left_join(convol_long, by = c("Country", "Year"))


# Save as a regular dataframe
capdata <- sourcedata
save(capdata, file = "cap_data.rda")

# Convert data to a panel dataframe
cappdata <- pdata.frame(sourcedata, index = c("Country", "Year"))

# Save as a panel dataframe
save(cappdata, file = "cap_pdata.rda")

```


# Titled Data
This code chunk renames the base data variables to have more descriptive and well-formatted titles. The renamed dataframes are saved as distinct variations of 'titledata', and stored in respective RDA files, which will be called upon widely across the shiny app in generation of various graphs and charts to more easily display meaningful titles for end users to understand the output visualizations. 
```{r titled_pdata}

# Load base dataframe
load("cap_data.rda")

# Load base dataframe
load("cap_data.rda")

# Rename Variables and Exclude Unwanted Columns
titledata <- capdata %>%
  rename(
    `Wine Production (Liters per Capita)` = WineProduction,
    `Wine Exports (Liters per Capita)` = WineExports,
    `Wine Imports (Liters per Capita)` = WineImports,
    `Real GDP per Capita (1990 Int'l $)` = RealGDP,
    `Exchange Rate` = Rate,
    `Wine Consumption (Liters per Adult)` = ConPerAdult
  ) %>%
  select(Country, Year,  # Include Country and Year for panel data
         `Wine Consumption (Liters per Adult)`, 
         `Wine Production (Liters per Capita)`,
         `Wine Exports (Liters per Capita)`,
         `Wine Imports (Liters per Capita)`,
         `Real GDP per Capita (1990 Int'l $)`,
         `Exchange Rate`)  # Reorder columns and exclude ConVol and ConPerCap

# Save as a regular dataframe
save(titledata, file = "title_data.rda")

# Convert data to a panel dataframe
titlepdata <- pdata.frame(titledata, index = c("Country", "Year"))

# Save as a panel dataframe
save(titlepdata, file = "title_pdata.rda")

```

# Choropleth Map
Upload supplement data of country geometries to support choropleth map creation. The uploaded csv contains country codes that correlate to their map geometries as defined in the Natural Earth dataset ("No permission is needed to use Natural Earth. Crediting the authors is unnecessary"). The data is then combined with wine consumption variables from our base data files.
```{r choropleth_map}

# Load base data
load('cap_pdata.rda')

# Load support data with built-in country geometries for country codes
codesdf <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv")

# Merge data to create dataframe for choropleth map
coded_panel <- merge(cappdata, codesdf, by.x = "Country", by.y = "COUNTRY", all.x = FALSE)

# Save the data frame to .rda files
save(coded_panel, file = "coded_panel.rda")

```

# Subset Panel Generation
This section of the code is the most user/decision intensive. It is where the user can change or add subsets created from the base data uploads to include specific variables they desire to examine further/jointly. The purpose of defining the subsets in this manner is to accomplish an efficient method of data wrangling to provide consistency in format for the data entering into functions we will build, as well as to be able to compare the significance of different sets of variables when we ultimately use them as the dependent and independent variables in our regression analysis.
```{r subset_panels}

# Load base data
load('cap_pdata.rda')

# Create subset panels for model analysis and comparison 

# Define chosen wine consumption variable as 'WineConsumption'
# Rename variables in regpdata
regpdata <- cappdata %>%
  rename(
    `WineConsumption` = ConPerAdult,
    `ExchangeRate` = Rate
  )

# To lag a variable: lag variables by 1 year and append to regpdata as new variables
regpdata$WineProductionLag <- lag(regpdata$WineProduction, 1)
regpdata$WineImportsLag <- lag(regpdata$WineImports, 1)
regpdata$WineConsumptionLag <- lag(regpdata$WineConsumption, 1)
# Remove year 1961 from the data to avoid missing values
time_index <- attr(regpdata, "index")[, "Year"]
regpdata62 <- regpdata[time_index != 1961, ]

# Specify variables of interest and store in vars
# Subset the data by vars
# Hold WineConsumption as first variable for looping consistency
# Store each data subset created in the panel_subsets list
panel_subsets <- list()

# Subset 1, regression: WineConsumption ~ WineProduction + WineExports + WineImports
vars <- c('WineConsumption', 'WineProduction', 'WineExports', 'WineImports')
pansub1 <- regpdata62[vars]
panel_subsets[[1]] <- pansub1

# Subset 2, regression: WineConsumption ~ WineProduction + WineExports + WineImports + RealGDP + ExchangeRate
vars <- c('WineConsumption', 'WineProduction', 'WineExports', 'WineImports', 'RealGDP', 'ExchangeRate')
pansub2 <- regpdata62[vars]
panel_subsets[[2]] <- pansub2

# Subset 3, regression: WineConsumption ~ lag(WineProduction) + WineExports + WineImports + RealGDP + ExchangeRate
vars <- c('WineConsumption', 'WineProductionLag', 'WineExports', 'WineImports', 'RealGDP', 'ExchangeRate')
pansub3 <- regpdata62[vars]
panel_subsets[[3]] <- pansub3

# Subset 4, regression: WineConsumption ~ WineProduction + WineExports + lag(WineImports) + RealGDP + ExchangeRate
vars <- c('WineConsumption', 'WineProduction', 'WineExports', 'WineImportsLag', 'RealGDP', 'ExchangeRate')
pansub4 <- regpdata62[vars]
panel_subsets[[4]] <- pansub4

# Subset 5, regression: WineConsumption ~ lag(WineProduction) + WineExports + lag(WineImports) + RealGDP + ExchangeRate
vars <- c('WineConsumption', 'WineProductionLag', 'WineExports', 'WineImportsLag', 'RealGDP', 'ExchangeRate')
pansub5 <- regpdata62[vars]
panel_subsets[[5]] <- pansub5


# Subset 6, regression: WineConsumption ~ lag(WineProduction) + WineExports + lag(WineImports) + RealGDP + lag(WineConsumption)
vars <- c('WineConsumption', 'WineProductionLag', 'WineExports', 'WineImportsLag', 'RealGDP', 'ExchangeRate', 'WineConsumptionLag')
pansub6 <- regpdata62[vars]
panel_subsets[[6]] <- pansub6

# Save the panel_subsets list to an .rda file
save(panel_subsets, file = "panel_subsets.rda")

# Save model formulas
model_formulas <- list(
  "Model 1"  = "Wine Consumption ~ Wine Production + Wine Exports + Wine Imports",
  "Model 2" = "Wine Consumption ~ Wine Production + Wine Exports + Wine Imports + Real GDP + Exchange Rate",
  "Model 3" = "Wine Consumption ~ Lagged Wine Production + Wine Exports + Wine Imports + Real GDP + Exchange Rate",
  "Model 4" = "Wine Consumption ~ Wine Production + Wine Exports + Lagged Wine Imports + Real GDP + Exchange Rate",
  "Model 5" = "Wine Consumption ~ Lagged Wine Production + Wine Exports + Lagged Wine Imports + Real GDP + Exchange Rate",
  "Model 6" = "Wine Consumption ~ Wine Production + Wine Exports + Wine Imports + Real GDP + Exchange Rate + Lagged Wine Consumption"
)

save(model_formulas, file = "model_formulas.rda")
```

## Regression Analysis
In this section of code we will define functions to dynamically apply regression analysis and statistical computations to the formatted data passed to them. We will apply the functions to run regressions and save our data to be called upon and displayed in the shiny app. Of note, the functions are built to be able to handle errors in model fitting and continue the program while providing useful and immediate feedback to the user regarding the performance of the equations passed to the regression function.

# Regression Functions
Define functions for use in regression analysis to effectively run regressions, capture model summaries and compute additional statistics, and save results.
```{r regression_functions}

## Regression Functions
# Function to perform regression and save model data
perform_regression <- function(subset_data, model_type) {
  dep_var <- 'WineConsumption'
  indep_vars <- setdiff(colnames(subset_data), dep_var)
  formula <- as.formula(paste(dep_var, "~", paste(indep_vars, collapse = " + ")))
  
  tryCatch({
    if (model_type == 'fixed') {
      model <- plm(formula, data = subset_data, model = 'within', effect = "twoways")
    } else {
      stop("Unknown model type")
    }
    
    # Extract fitted values and residuals
    fitted_values <- as.numeric(fitted(model))
    residuals <- as.numeric(residuals(model))
    
    # Compute ACF of residuals
    acf_values <- acf(residuals, plot = FALSE)$acf
    
    if (length(fitted_values) != nrow(subset_data) || length(residuals) != nrow(subset_data)) {
      stop("Length of fitted values or residuals does not match the number of rows in the data.")
    }
    
    return(list(
      model = model,
      fitted_values = fitted_values,
      residuals = residuals,
      acf = acf_values,
      formula = as.character(formula)  # Save the formula as a string
    ))
  }, error = function(e) {
    cat("Error occurred during model fitting:\n", conditionMessage(e), "\n")
    return(NULL)
  })
}

compute_aic_bic <- function(model) {
  if (inherits(model, "plm") || inherits(model, "lm")) {
    n <- length(model$residuals)
    k <- length(coef(model))
    logLik <- sum(dnorm(model$residuals, mean = 0, sd = sd(model$residuals), log = TRUE))
    aic <- -2 * logLik + 2 * k
    bic <- -2 * logLik + log(n) * k
  } else {
    stop("Unknown model type for AIC/BIC computation")
  }
  return(c(AIC = aic, BIC = bic))
}


# Function to perform Breusch-Pagan test for heteroscedasticity
perform_breusch_pagan_test <- function(model) {
  if (inherits(model, "plm") || inherits(model, "lm")) {
    test_result <- bptest(model, studentize = TRUE)
    return(list(
      p_value = test_result$p.value,
      test_statistic = test_result$statistic,
      test_name = "Breusch-Pagan Test"
    ))
  } else {
    stop("Unknown model type for Breusch-Pagan test")
  }
}

summarize_model <- function(model_data) {
  if (is.null(model_data)) {
    return(NULL)
  }
  
  model <- model_data$model
  fitted_values <- model_data$fitted_values
  residuals <- model_data$residuals
  acf_values <- model_data$acf
  
  # Extract model summary
  model_summary <- tryCatch({
    summary(model)
  }, error = function(e) {
    cat("Error summarizing model:", conditionMessage(e), "\n")
    return(NULL)
  })
  
  r_squared <- if (!is.null(model_summary)) model_summary$r.squared["rsq"] else NA
  adj_r_squared <- if (!is.null(model_summary)) model_summary$r.squared["adjrsq"] else NA
  f_statistic <- if (!is.null(model_summary)) model_summary$fstatistic$statistic["F"] else NA
  
  aic_bic <- compute_aic_bic(model)
  aic_value <- aic_bic["AIC"]
  bic_value <- aic_bic["BIC"]
  
  panel_data_index <- tryCatch({
    as.data.frame(index(model$residuals))
  }, error = function(e) {
    cat("Error indexing model residuals:", conditionMessage(e), "\n")
    return(NULL)
  })
  if (!is.null(panel_data_index)) {
    colnames(panel_data_index) <- c("Country", "Year")
  }
  
  residuals_df <- tryCatch({
    data.frame(panel_data_index, Residuals = residuals)
  }, error = function(e) {
    cat("Error creating residuals data frame:", conditionMessage(e), "\n")
    return(NULL)
  })
  
  fitted_values_df <- tryCatch({
    data.frame(panel_data_index, FittedValues = fitted_values)
  }, error = function(e) {
    cat("Error creating fitted values data frame:", conditionMessage(e), "\n")
    return(NULL)
  })
  
  combined_df <- tryCatch({
    merge(residuals_df, fitted_values_df, by = c("Country", "Year"))
  }, error = function(e) {
    cat("Error merging residuals and fitted values data frames:", conditionMessage(e), "\n")
    return(NULL)
  })
  
  model_stats <- data.frame(
    R_Squared = r_squared,
    Adj_R_Squared = adj_r_squared,
    F_Statistic = f_statistic,
    AIC = aic_value,
    BIC = bic_value
  )
  
  # Compute robust standard errors
  robust_se <- tryCatch({
    coeftest(model, vcov. = vcovHC(model, type = "HC1"))
  }, error = function(e) {
    cat("Error computing robust standard errors:", conditionMessage(e), "\n")
    return(NULL)
  })
  
  # Extract Breusch-Pagan test results
  breusch_pagan_test <- tryCatch({
    perform_breusch_pagan_test(model)
  }, error = function(e) {
    cat("Error performing Breusch-Pagan test:", conditionMessage(e), "\n")
    return(NULL)
  })
  
  return(list(
    tidy = tidy(model),
    model_stats = model_stats,
    combined_data = combined_df,
    acf = acf_values,
    formula = model_data$formula,
    robust_se = robust_se,  # Include robust standard errors
    breusch_pagan_test = breusch_pagan_test  # Include Breusch-Pagan test results
  ))
}


```

# Model Processing
Use the functions defined above to generate and save comprehensive model summaries and statistics.
```{r model_analysis}

## Model Processing
# Load the panel_subsets list from the .rda file
load("panel_subsets.rda")

# Initialize lists for model data and summaries
fitted_models <- list()
model_summaries <- list()

# Initialize the number of subsets
num_subsets <- length(panel_subsets)

# Model Processing
for (i in 1:num_subsets) {
  subset_data <- panel_subsets[[i]]
  cat("Processing subset", i, "with", nrow(subset_data), "rows and", ncol(subset_data), "columns.\n")
  
  # Fit and summarize fixed effects model
  fixed_model_data <- perform_regression(subset_data, 'fixed')
  
  if (!is.null(fixed_model_data)) {
    fitted_models[[paste0("Model_", i, "_fixed")]] <- fixed_model_data
    
    # Compute robust standard errors for fixed model
    robust_se <- tryCatch({
      coeftest(fixed_model_data$model, vcov. = vcovHC(fixed_model_data$model, type = "HC1"))
    }, error = function(e) {
      cat("Error computing robust standard errors for model", i, ":", conditionMessage(e), "\n")
      NULL
    })
    
    # Add robust standard errors to model data
    fixed_model_data$robust_se <- robust_se
    
    model_summary <- tryCatch({
      summarize_model(fixed_model_data)
    }, error = function(e) {
      cat("Error summarizing model", i, ":", conditionMessage(e), "\n")
      NULL
    })
    
    model_summaries[[paste0("Model_", i)]] <- model_summary
    if (!is.null(model_summary)) {
      cat("Fixed effects model", i, "fitted and summarized successfully.\n")
    } else {
      cat("Fixed effects model", i, "could not be summarized.\n")
    }
  }
}

# Save the model summaries to an RData file
save(model_summaries, file = "reg_summaries.rda")

# Combine model_stats into a single data frame for comparison
model_statistics <- bind_rows(lapply(model_summaries, function(x) x$model_stats), .id = "Model")
# Save the model_statistics
save(model_statistics, file = "model_statistics.rda")

# Save model_stats_combined
save(model_statistics, file = "model_statistics.rda")


```


```{r robuest_errors}

# Function to extract robust standard errors from model
extract_robust_se <- function(model_summary) {
  if (is.null(model_summary)) {
    return(NULL)
  }
  
  # Extract robust standard errors
  robust_se <- model_summary$robust_se
  
  if (is.null(robust_se)) {
    return(NULL)
  }
  
  return(robust_se)
}

# Load model summaries from .rda file
load("reg_summaries.rda")

# Initialize a list to store robust standard errors
robust_se_list <- list()

# Process each model summary and store robust standard errors in the list
for (model_name in names(model_summaries)) {
  model_summary <- model_summaries[[model_name]]
  
  # Extract robust standard errors for the current model
  robust_se <- extract_robust_se(model_summary)
  
  if (!is.null(robust_se)) {
    robust_se_list[[model_name]] <- robust_se
  } else {
    cat("No robust standard errors available for", model_name, "\n")
  }
}

# Save the list of robust standard errors to an RData file
save(robust_se_list, file = "robust_se_list.rda")

# Example to verify the saved data
load("robust_se_list.rda")

# Option to print data to verify current output is equivalent to manual upload below
# print(robust_se_list)


# Model 1 data
model_1_data <- data.frame(
  Variable = c("WineProduction", "WineExports", "WineImports"),
  Estimate = c(0.80810363, -0.90902453, 0.00098722),
  Std_Error = c(0.07967459, 0.11980043, 0.00037394),
  t_value = c(10.1426, -7.5878, 2.6400),
  Pr_It = c("< 2.2e-16", "5.554e-14", "0.008372"),
  stringsAsFactors = FALSE
)
save(model_1_data, file = "robust_se_model_1.rda")

# Model 2 data
model_2_data <- data.frame(
  Variable = c("WineProduction", "WineExports", "WineImports", "RealGDP", "ExchangeRate"),
  Estimate = c(8.2186e-01, -9.1181e-01, 9.5174e-04, 2.0516e-06, -9.2946e-03),
  Std_Error = c(8.4032e-02, 1.1820e-01, 3.7534e-04, 3.6152e-04, 5.0233e-03),
  t_value = c(9.7803, -7.7138, 2.5357, 0.0057, -1.8503),
  Pr_It = c("< 2.2e-16", "2.161e-14", "0.01132", "0.99547", "0.06446"),
  stringsAsFactors = FALSE
)
save(model_2_data, file = "robust_se_model_2.rda")

# Model 3 data
model_3_data <- data.frame(
  Variable = c("WineProduction", "WineExports", "WineImports", "RealGDP", "ExchangeRate"),
  Estimate = c(9.0280e-01, -1.0528e+00, 1.1794e-03, -8.6343e-05, -1.0112e-02),
  Std_Error = c(7.4703e-02, 9.8408e-02, 2.9078e-04, 3.2083e-04, 2.8818e-03),
  t_value = c(12.0852, -10.6981, 4.0560, -0.2691, -3.5089),
  Pr_It = c("< 2.2e-16", "< 2.2e-16", "5.238e-05", "0.7878704", "0.0004627"),
  stringsAsFactors = FALSE
)
save(model_3_data, file = "robust_se_model_3.rda")

# Model 4 data
model_4_data <- data.frame(
  Variable = c("WineProduction", "WineExports", "WineImports", "RealGDP", "ExchangeRate"),
  Estimate = c(8.1117e-01, -9.1096e-01, 8.5027e-04, 6.1822e-05, -9.2156e-03),
  Std_Error = c(8.6609e-02, 1.2103e-01, 4.1016e-04, 3.7101e-04, 5.1470e-03),
  t_value = c(9.3658, -7.5267, 2.0729, 0.1666, -1.7905),
  Pr_It = c("< 2.2e-16", "8.744e-14", "0.03834", "0.86768", "0.07357"),
  stringsAsFactors = FALSE
)
save(model_4_data, file = "robust_se_model_4.rda")

# Model 5 data
model_5_data <- data.frame(
  Variable = c("WineProduction", "WineExports", "WineImports", "RealGDP", "ExchangeRate"),
  Estimate = c(8.8050e-01, -1.0455e+00, 9.3431e-04, 4.2905e-05, -1.0061e-02),
  Std_Error = c(7.7727e-02, 1.0477e-01, 3.2467e-04, 3.3360e-04, 3.1796e-03),
  t_value = c(11.3281, -9.9789, 2.8777, 0.1286, -3.1643),
  Pr_It = c("< 2.2e-16", "< 2.2e-16", "0.004060", "0.897683", "0.001585"),
  stringsAsFactors = FALSE
)
save(model_5_data, file = "robust_se_model_5.rda")

# Model 6 data
model_6_data <- data.frame(
  Variable = c("WineProduction", "WineExports", "WineImports", "RealGDP", "ExchangeRate", "WineConsumption"),
  Estimate = c(6.5726e-02, -9.3893e-02, 6.8657e-05, 2.9159e-05, -1.4923e-03, 9.0414e-01),
  Std_Error = c(1.9579e-02, 2.1315e-02, 2.5333e-05, 5.0375e-05, 4.058e-04, 2.1454e-02),
  t_value = c(3.3569, -4.4051, 2.7102, 0.5788, -4.3816, 42.1426),
  Pr_It = c("0.0008072", "1.129e-05", "0.0067982", "0.5627788", "1.257e-05", "< 2.2e-16"),
  stringsAsFactors = FALSE
)
save(model_6_data, file = "robust_se_model_6.rda")

```

